Commutative Character Sheaves

### 2015-11-09 followup.tex
Working on Section 2

We recall some facts about the abelianization of a smooth group scheme $G$.
Let $G\der \hookrightarrow G$ denote the closed subgroup generated by the family of smooth morphisms
$c_n: (G\times G)^n \to G$ given by $c_1: (x,y)\mapsto xyx^{-1}y^{-1}$ and ...
%Then $G \times G \to G\der$ is a dominant morphism \cite{SGA3}*{Expos\'e {VI}$_B$, \S 7.2}.
The group scheme $G$ is commutative if and only if $G\der$ is trivial.
When $G$ is not connected, $G\der$ need not be connected, though it is smooth.
%The restriction of $G\times G\to G\der$ to identity components gives a dominant morphism $G^0\times G^0 \to G^0\der$ \cite{SGA3}*{Expos\'e {VI}$_B$, Prop. 7.8}.

The quotient $G\ab\ceq G/G\der$ exists in schemes over $\Fq$.
%and the quotient $q : G \to G\ab$ is faithfully flat and a $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
We summarize the setup in a diagram.
\[
\begin{tikzcd}
{} & G\times G \arrow{d}{c} &&&\\
1 \arrow{r} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
\end{tikzcd}
\]

@@

%\todo{I got this wrong. I think our sheaves are not extra information in the commutative case. Masound's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case. So, I think the modification is easy: add mop to diagram 2.4 in Masoud's paper. \\ -CC}

@@

@@

In this section we use descent along the abelianization $q : G \to G\ab$ to prove Propositions~1.2 and 1.4, and Theorem~\ref{thm:Gab}.
This approach requires introducing equivariant linear character sheaves, as defined in Section~[].

@@

Let $G$ be as above.
Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
Let $a : H \times G\to G$ be a group action compatible with the group structure on $G$ and write $p : H\times G \to G$ for projection. 
Consider the morphisms
\[
\begin{tikzcd}
H \times H \times G 
\arrow[shift left=4]{r}{b_1, b_2, b_3} 
\arrow{r}{}
\arrow[shift right=4]{r}{} 
& H \times G 
\arrow[shift left=2]{r}{a}
\arrow[shift right=2]{r}[swap]{p}
 & G 
\end{tikzcd}
\]
defined by $b_1(h_1,h_2,g) = (n(h_1,h_2),g)$,  $b_2(h_1,h_2,g) = (h_1,a(h_2,g))$ and $b_3(h_1,h_2,g) = (h_2,g)$.
Then, $a\circ b_1 = a\circ b_2$ and $a\circ b_3 = p\circ b_2$ and $p\circ b_1 = p\circ b_3$.
An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
\[
\nu : a^*\cs{L} \to p^*\cs{L}
\] 
of Weil local systems on $H\times G$ such that the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes,
\[
\begin{tikzcd}
\ &  \arrow{dl}[swap]{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}{p\circ b_2 = a\circ b_3} & \\
b_1^* a^*\, \mathcal{L} \arrow{dr}[swap]{b_1^*(\nu)} &&&&   \arrow{dl}{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L}, & 
\end{tikzcd}
\]
and $s^*(\nu) = \id_{\cs{L}}$.
In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations above; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
\iffalse
We remark that, on stalks, this condition is ...
\[
\begin{tikzcd}
\ &  \cs{L}_{x\cdot(y\cdot z)} \arrow{r}{\nu_{x,y\cdot z}} & \cs{L}_{y\cdot z} & \\
\cs{L}_{(x\cdot y)\cdot z} \arrow{dr}[swap]{\nu_{x\cdot y,z}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{y,z}} \cs{L}_{y\cdot z} \\
& \cs{L}_z \arrow[equal]{r} & \cs{L}_z & 
\end{tikzcd}
\]
\fi
%
Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
\[
\begin{tikzcd}
\arrow{d}[swap]{\nu} a^*\cs{L} \arrow{r}{a^*(\alpha)} & a^*\cs{L}' \arrow{d}{\nu'} \\
p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
\end{tikzcd}
\]
commutes.
This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.

@@

An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense. 
Consider the following morphisms: $c_0 : H\times G \times G\to H\times G \times H \times G$ defined by $c_0(h,g_1,g_2)\ceq(h,g_1,h,g_2)$;
$c_1 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),a(h,g_2))$;  $c_2 : H \times G\times G \to H\times G$ defined by $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$; and $c_3 : H \times G\times G \to G\times G$ defined by $c_3(h, g_1, g_2) = (g_1, g_2)$. 
Then $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ if $(\cs{L},\mu)$ is a linear character sheaf on $G$ and the following diagram of Weil local systems on $H \times G\times G$ commutes.
\[
\begin{tikzcd}
\arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} & \arrow{l}[swap]{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{r}{p\circ c_2 = m\circ c_3}  & c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_i\circ c_1 = a\circ p_i\circ c_0} & c_0^*(a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{c_0^*(\nu\boxtimes \nu)} & c_0^*(p^*\cs{L} \boxtimes p^*\cs{L}) & \arrow{l}[swap]{p\circ p_i\circ c_0 = p_i \circ c_3}c_3^*(\cs{L}\boxtimes \cs{L})
\end{tikzcd}
\]
%In this diagram, the arrows not labeled are derived from canonical isomorphisms.
%\iffalse
On stalks, this condition is
\[
\begin{tikzcd}
\arrow{d}[swap]{\mu_{(h\cdot g_1, h\cdot g_2)}} \cs{L}_{(h\cdot g_1)(h\cdot g_2)} & \arrow[equal]{l}  \cs{L}_{h\cdot(g_1 g_2)} \arrow{r}{\nu_{(h, g_2 g_2)}} & \cs{L}_{g_1 g_2} \arrow[equal]{r} & \cs{L}_{g_1 g_2} \arrow{d}{\mu_{(g_1,g_2)}} \\
\cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow[equal]{r} & \cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow{r}{\nu_{(h,g_1)}\otimes \nu_{(h,g_2)}} & \cs{L}_{g_1}\otimes \cs{L}_{g_2} & \arrow[equal]{l} \cs{L}_{g_1} \otimes \cs{L}_{g_2},
\end{tikzcd}
\]
for all $(h,g_1,g_2)\in H\times G\times G$.
%\fi
%
A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves, so
\[
\begin{tikzcd}
\arrow{d}{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
\end{tikzcd}
\]
commutes.
%
Let $\CS_H(G)$ be the category of $H$-equivariant linear character sheaves on $G$.

@@

If $(\cs{L},\mu,\nu)$ and $(\cs{L},\mu,\nu')$ in $\CS_H(G)$, then $\nu = \nu'$?

@@

Now suppose $q : G \to G'$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
\[
\begin{tikzcd}
H\times G
 \arrow[shift left=2]{r}{a}
  \arrow[shift right=2,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
G'
\end{tikzcd}
\]
Let $\cs{L}'$ be a linear character sheaf on $G'$.
Consider the functor
\[
q^* : \CS(G') \to \CS(G)
\]
given on objects by $(\cs{L}',\mu') \mapsto (q^*\cs{L}', (q\times q)^* \mu', \nu_{\cs{L}'})$; cf [Dictionary].
Then $q^*\cs{L}'$ is an $H$-equivariant linear character sheaf on $G$ when equipped with the canonical isomorphism
\[
\nu_{\cs{L}'} : a^* q^* \cs{L}' \mathop{\longrightarrow}\limits^{\iso} (q\circ a)^* \cs{L}' = (q\circ p)^*\cs{L}' \mathop{\longrightarrow}\limits^{\iso} p^* q^*\cs{L}.
\]
This simple observation shows that the functor $q^* : \CS(G') \to \CS(G)$  factors according to the following commuting diagram of functors
\[
\begin{tikzcd}
\CS(G) &&\arrow{ll}[swap]{q^*} 
\CS(G') \arrow{dl}{\text{`comparison'}}\\
& \arrow{ul}{\text{forget}} \CS_{H}(G). & 
\end{tikzcd}
\]

@@

\begin{proof}
. . . 
So the lemma reduces to the claim: the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence. 
To see this, observe first that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
Moreover, if $Y \to X$ is a flat surjective morphism of affine schemes over $\Fq$, then the comparison functor $\Loc(X) \to \Loc(Y\to X)$ is an equivalence, with $\Loc(Y\to X)$ defined as in [].
It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fppf topology.
(This is a small variation on the proof of the fact that quasicoherent sheaves form a stack on sheaves in the fppf topology.)
Since $q : G\to G'$ is an $H$-torsor in the fppf topology, is now follows from descent theory that the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence.
\end{proof}

@@

In this section we consider a different perspective on $\CS_H(G)$ of $\CS(G)$ which will help us understand how the forgetful functor $\CS_H(G) \to \CS(G)$ induces an equivalence $\CS_H(G) \to \CS'(G)$, in the case required to prove Proposition~1.2.

Suppose there is some $f : H\times G\to G\times G$ such that the following diagram commutes.
%%%%%%%% FIX!!!! %%%%%%%%%%
\[
\begin{tikzcd}
\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
G & & G \\
& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p} & 
\end{tikzcd}
\]
Then $f(h,g) = (a(h,g) g^{-1}, g)$.
Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq a(h,g) g^{-1}$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.

Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ defines an isomorphism $\beta : f_1^*\cs{L} \to (\EE)_{H\times G}$ by $\beta \boxtimes \id = \nu \circ f^*(\mu)^{-1}$ from which $\nu$ may be recovered. 
In this way we see we may replace $(\cs{L},\mu,\nu)$ with another triple, $(\cs{L},\mu,\beta)$.
What are the defining properties of $\beta$?

Now,

Let $\CS'(G)$ be the full subcategory of $\CS(G)$ consisting of those $(\cs{L},\mu,\nu) \in \CS_H(G)$ such that $f_1^*\cs{L} \iso (\EE)_{H\times G}$.

@@

As we have seen above, the fppf quotient $q : G\to G\ab = G/G\der$ exists in schemes.
Moreover, the quotient $q : G \to G\ab$ is faithfully flat and a $G\der$-torsor in the fppf topology, by\cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}
%(In fact, it's a trivial torsor in that topology.)
It now follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
On the other hand, by Lemma~[], the forgetful functor $\CS_{G\der}(G)\to \CS(G)$ defines an equivalence $\CS_{G\der}(G)\to \CS'(G)$, where $\CS'(G)$ is the category of $(\cs{L},\mu,\nu)\in \CS_{G\der}(G)$ such that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
It now follows that $q^* : \CS(G\ab) \to \CS(G)$ is fll and faithful with essential image $\CS'(G)$.
\end{proof}

>>>>

We recall some facts about the abelianization of a smooth group scheme $G$.
Let $G\der \hookrightarrow G$ denote the closed subgroup generated by the smooth morphism
$G\times G \to G$ given by $c: (x,y)\mapsto xyx^{-1}y^{-1}$. Then
$G \times G \to G\der$ is a dominant morphism \cite{SGA3}*{Expos\'e {VI}$_B$, \S 7.2}.
Moreover, $G$ is commutative if and only if $G\der$ is trivial.
When $G$ is not connected, $G\der$ need not be connected, though it is smooth.
The restriction of $G\times G\to G\der$ to identity components gives a dominant
morphism $G^0\times G^0 \to G^0\der$ \cite{SGA3}*{Expos\'e {VI}$_B$, Prop. 7.8}.

The quotient $G\ab\ceq G/G\der$ exists in schemes over $\Fq$, and the quotient $q : G \to G\ab$
is faithfully flat and a $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
We summarize the setup in a diagram.
\[
\begin{tikzcd}
{} & G\times G \arrow{d}{c} &&&\\
1 \arrow{r} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
\end{tikzcd}
\]

@@

%\todo{I got this wrong. I think our sheaves are not extra information in the commutative case. Masoud's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case. So, I think the modification is easy: add mop to diagram 2.4 in Masoud's paper. \\ -CC}

@@

In this section we show that trace of Frobenius is an isomorphism for commutative character sheaves on a
smooth commutative group scheme $G$.  We begin by reinterpreting Definition \ref{def:CCScom} in terms of
cocycles.

@@

In this section we use descent along the abelianization $q : G \to G\ab$ to prove Propositions~1.2 and 1.4, and Theorem~\ref{thm:Gab}.

@@

Let $G$ be as above.
Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
Let $a : H \times G\to G$ be a group action compatible with the group structure on $G$ and write $p : H\times G \to G$ for projection. 
Consider the morphisms
\[
\begin{tikzcd}
H \times H \times G 
\arrow[shift left=4]{r}{b_1, b_2, b_3} 
\arrow{r}{}
\arrow[shift right=4]{r}{} 
& H \times G 
\arrow[shift left=4]{r}{a}
\arrow[shift right=4]{r}[swap]{p}
 & G 
\end{tikzcd}
\]
defined by $b_1(h_1,h_2,g) = (n(h_1,h_2),g)$,  $b_2(h_1,h_2,g) = (h_1,a(h_2,g))$ and $b_3(h_1,h_2,g) = (h_2,g)$.
Then, $a\circ b_1 = a\circ b_2$ and $a\circ b_3 = p\circ b_2$ and $p\circ b_1 = p\circ b_3$.
An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
\[
\nu : a^*\cs{L} \to p^*\cs{L}
\] 
of Weil local systems on $H\times G$ such that the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes,
\[
\begin{tikzcd}
\ &  \arrow{dl}[swap]{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}{p\circ b_2 = a\circ b_3} & \\
b_1^* a^*\, \mathcal{L} \arrow{dr}[swap]{b_1^*(\nu)} &&&&   \arrow{dl}{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L}, & 
\end{tikzcd}
\]
and $s^*(\nu) = \id_{\cs{L}}$.
In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations above; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
\iffalse
We remark that, on stalks, this condition is ...
\[
\begin{tikzcd}
\ &  \cs{L}_{x\cdot(y\cdot z)} \arrow{r}{\nu_{x,y\cdot z}} & \cs{L}_{y\cdot z} & \\
\cs{L}_{(x\cdot y)\cdot z} \arrow{dr}[swap]{\nu_{x\cdot y,z}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{y,z}} \cs{L}_{y\cdot z} \\
& \cs{L}_z \arrow[equal]{r} & \cs{L}_z & 
\end{tikzcd}
\]
\fi
%
Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
\[
\begin{tikzcd}
\arrow{d}[swap]{\nu} a^*\cs{L} \arrow{r}{a^*(\alpha)} & a^*\cs{L}' \arrow{d}{\nu'} \\
p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
\end{tikzcd}
\]
commutes.
This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.

@@

An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense. 
Consider the morphisms $c_1 : H \times G\times G \to G\times G$, $c_2 : H \times G\times G \to H\times G$ and $c_3 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),a(h,g_2))$ and $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$ and $c_3(h, g_1, g_2) = (g_1, g_2)$. 
Then $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ if $(\cs{L},\mu)$ is a linear character sheaf on $G$ and the following diagram of Weil local systems on $H \times G\times G$ commutes.
\[
\begin{tikzcd}
\arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} & \arrow{l}[swap]{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{r}{p\circ c_2 = m\circ c_3}  & c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{r} & (p^*\cs{L}) \boxtimes (p^*\cs{L}) & \arrow{l}[swap]{\nu\boxtimes \nu}  (a^*\cs{L}) \boxtimes (a^*\cs{L}) & \arrow{l} c_3^*(\cs{L}\boxtimes \cs{L})
\end{tikzcd}
\]
In this diagram, the arrows not labeled are derived from canonical isomorphisms.
\iffalse
On stalks, this condition is
\[
\begin{tikzcd}
\ &  \cs{L}_{h\cdot (xy)} \arrow{r}{} & \cs{L}_{xy} & \\
\cs{L}_{(h\cdot x)(h\cdot y)} \arrow{dr}[swap]{} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{} \cs{L}_{xy} \\
& \cs{L}_{h\cdot x}\otimes \cs{L}_{h\cdot y} \arrow{r} & \cs{L}_x\otimes \cs{L}_y & 
\end{tikzcd}
\]
\fi
%
A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves, so
\[
\begin{tikzcd}
\arrow{d}{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
\end{tikzcd}
\]
commutes.
%
Let $\CS_H(G)$ be the category of $H$-equivariant linear character sheaves on $G$.

@@

@@

Now suppose $q : G \to G'$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
\[
\begin{tikzcd}
H\times G
 \arrow[shift left=4]{r}{a}
  \arrow[shift right=4,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
G'
\end{tikzcd}
\]
Let $\cs{L}'$ be a linear character sheaf on $G'$.
Consider the functor
\[
q^* : \CS(G') \to \CS(G)
\]
given on objects by $(\cs{L}',\mu') \mapsto (q^*\cs{L}', (q\times q)^* \mu', \nu_{\cs{L}'})$; cf [Dictionary].
Then $q^*\cs{L}'$ is an $H$-equivariant linear character sheaf on $G$ when equipped with the canonical isomorphism
\[
\nu_{\cs{L}'} : a^* q^* \cs{L}' \mathop{\longrightarrow}\limits^{\iso} (q\circ a)^* \cs{L}' = (q\circ p)^*\cs{L}' \mathop{\longrightarrow}\limits^{\iso} p^* q^*\cs{L}.
\]
This simple observation shows that the functor $q^* : \CS(G') \to \CS(G)$  factors according to the following commuting diagram of functors
\[
\begin{tikzcd}
\CS(G) &&\arrow{ll}[swap]{q^*} 
\CS(G') \arrow{dl}{\text{`comparison'}}\\
& \arrow{ul}{\text{forget}} \CS_{H}(G). & 
\end{tikzcd}
\]

@@

\begin{proof}
. . . 
So the lemma reduces to the claim: the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence. 
To see this, observe first that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
Moreover, if $Y \to X$ is a flat surjective morphism of affine schemes over $\Fq$, then the comparison functor $\Loc(X) \to \Loc(Y\to X)$ is an equivalence, with $\Loc(Y\to X)$ defined as in [].
It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fppf topology.
(This is a small variation on the proof of the fact that quasicoherent sheaves form a stack on sheaves in the fppf topology.)
Since $q : G\to G'$ is an $H$-torsor in the fppf topology, is now follows immediately that the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence.
\end{proof}

@@

In this section we find a subcategory $\CS'(G)$ of $\CS(G)$ such that the forgetful functor $\CS_H(G) \to \CS(G)$ induces an equivalence $\CS_H(G) \to \CS'(G)$, in the case required to prove Proposition~1.2.

Suppose there is some $f : H\times G\to G\times G$ such that the following diagram commutes.
%%%%%%%% FIX!!!! %%%%%%%%%%
%\[
%\begin{tikzcd}
%&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
%G & & G \\
%& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p} & 
%\end{tikzcd}
%\]
Then $f(h,g) = (f_1(h,g),p)$ for $f_1 : H\times G \to G$.
Let $\CS'(G)$ be the full subcategory of $\CS(G)$ consisting of those $(\cs{L},\mu,\nu) \in \CS_H(G)$ such that $f_1^*\cs{L} \iso (\EE)_{H\times G}$.

@@

As we have seen above, the fppf quotient $q : G\to G\ab = G/G\der$ exists in schemes and is a $G\der$-torsor in the fppf topology. 
%(In fact, it's a trivial torsor in that topology.)
It follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
On the other hand, by Lemma~[], the forgetful functor $\CS_{G\der}(G)\to \CS(G)$ defines an equivalence $\CS_{G\der}(G)\to \CS'(G)$, where $\CS'(G)$ is the category of $(\cs{L},\mu,\nu)\in \CS_{G\der}(G)$ such that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
It now follows that $q^* : \CS(G\ab) \to \CS(G)$ is fll and faithful with essential image $\CS'(G)$.
\end{proof}
